---
title: "Prediction Assignment"
author: "guchiguchi"
date: "2018/5/19"
output: html_document
---

###libraries
```{r message=FALSE}
library(tidyverse)
library(caret)
library(rattle)
```
  
#check and preparing data
  
  load csv file
```{r message=FALSE}
pml_training <- read_csv("https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv", 
    na = "0")
pml_testing <- read_csv("https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv", 
    na = "0")
```
  
  check dimention
```{r}
dim(pml_training); dim(pml_testing)
```
  
```{r}
pml_training %>% count(user_name, classe)
```
  

  check na's
```{r}
count_na <- function(x){
  x %>% is.na() %>% sum() 
}
data.frame(NA_count = sapply(pml_training,FUN = count_na), class = sapply(pml_training, class)) -> data_class
data_class %>% count(class)
```

  convert class character to numeric(7:159)
```{r message=FALSE, warning=FALSE}
ix <- 7:150
pml_training[ix] <- sapply(pml_training[ix], as.numeric)
```
  
  
  
  Training data separate training and test.
  
  We do not need 
  "X1", "user_name", "raw_timestamp_part_1", "raw_timestamp_part_2", "cvtd_timestamp"
  
  Delete them.
  
```{r}
pml_training <-  pml_training[,6:160]
#pml_training$classe <- as.factor(pml_training$classe)
```
  
  create training and testing data.
```{r}
set.seed(20180520)
inTrain <- createDataPartition(y = pml_training$classe, p=0.7, list=FALSE)
training_training <- pml_training[inTrain,]
training_testing <- pml_training[-inTrain,]
```
  
  train by rapart.
```{r}
training_training %>% mutate_all(funs(ifelse(is.na(.),0,.))) -> training_NaToZero
training_testing %>% mutate_all(funs(ifelse(is.na(.),0,.))) -> testing_NaToZero

mod_rapart <- train(data = training_NaToZero,
              classe ~.,
              method = "rpart")

print(mod_rapart$finalModel)
```
  file:///Users/aa575274/Documents/cousera/courses/08_PracticalMachineLearning/019predictingWithTrees/index.html#15
  
  
```{r}
fancyRpartPlot(mod_rapart$finalModel)
```
  
  
  
  train by randomforest.
```{r}
mod_rf <- train(data = training_NaToZero,
              classe ~.,
              trControl = trainControl(method="oob"), method = "rf")

# mod_gam <- train(data = a,
#               classe ~.,
#               method = "gam")

#xgboost
# mod_xgt <- train(data = a,
#               classe ~.,
#               method = "xgbTree")
# 
# mod_xgl <- train(data = a,
#               classe ~.,
#               method = "xgbLinear")

```
  
  
#check prediction

```{r}
pred_rpar <- predict(mod_rapart, newdata = testing_NaToZero)
pred_rf <- predict(mod_rf, newdata = testing_NaToZero)
```
  
  
  
```{r}
confusionMatrix(data = pred_rpar, testing_NaToZero$classe %>% as.factor())
confusionMatrix(data = pred_rf, testing_NaToZero$classe %>% as.factor())
```
  
  Random forest is good model
  

#check testing data and answer the Course Project Prediction Quiz
  
  prepare pml_testing data
```{r message=FALSE, warning=FALSE}
ix <- 7:150
pml_testing[ix] <- sapply(pml_testing[ix], as.numeric)
pml_testing <-  pml_testing[,6:160]
pml_testing  %>% mutate_all(funs(ifelse(is.na(.),0,.))) -> pml_testing_NaToZero
```
  
  predict Course Project Prediction Quiz
```{r}
pred_rf_test <- predict(mod_rf, newdata = pml_testing_NaToZero)
pred_rf_test
```
 